Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
More corrections
@JJ have a look to last changes when you have time, I will come back
Sunday night, so we have all Monday.
Revising the introduction.
Mainly first paragraphs.

% IEAs
Interactive evolutionary computation (IEC) systems are, in general, evolutionary methods
whose fitness evaluations are performed by humans through an interactive 
system \cite{eiben2015interactive}.
They are usually applied in problems where the fitness function is not known or simply
does not exist, and the result of optimization should fit a certain human need or desire. 
That is why their use-case includes the evolution of objects with subjective characteristics
such visual appeal or attractiveness \cite{biomorphs} as well as others where human behavior is 
considered, for instance the optimization of teamwork \cite{kosorukoff2002evolutionary}
or creativity \cite{yu2011cooks}.
% Human Based Computation
These IEC systems are an interesting venue of research, since they have demonstrated 
their ability for effectively 
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992,evoeco},
as well as other artifacts in many other domains \cite{ie1}. In those cases when 
human interaction is responsible of other 
aspects of the evolutionary process, some authors classify these IEC methods 
as human-based evolutionary computation \cite{kosorukoff2001human} 
or as human-based computation \cite{quinn2011human}.
% Problems
However, the necessary intervention of humans, brings certain challenges 
to designers of IEC methods namely, human evaluations are slow and expensive, there is
human fatigue caused by the interaction \cite{ie1}, and also boredom arise
when users evaluate a large number of phenotypes, 
many of which are not interesting or are very similar to each other.
% C-IEAs
Moreover, the performance of these systems effectively depends on the number of users
they are able to include; to reach more users,
IEC systems are some times developed as web applications depending on web visitors to help
with the search, using both anonymous and registered users. Some systems 
employ a collaborative technique, where several users participate in 
the evaluation, this method is called Collaborative-IEC (C-IEC)
\cite{picbreeder,seyama2016development,wagy2014collective}.
% Volunteers 
Having a volunteer system can lower the requirements for anyone to participate in
the experiment thus increasing the {\em performance} of the whole system. But using a volunteer based 
system raises other issues \cite{sarmenta2001volunteer,web:BOINC}, such as the 
volunteer\'s lack of accountability, and the need to build trust between participants and project
owners. Other issues for project owners are also the difficulty of establishing 
the amount of time and resources a volunteer is willing to spend on the system, 
and how they decide if they participate or not \cite{JJ:2016}.

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/framework.eps}
    \caption{IEC Human-centered framework.}
    \label{fig:hc_framework}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=4in]{img/weibull_2.png}
    \caption{Experiment G. Weibull Fit}
    \label{fig:w2}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=4in]{img/weibull_3.png}
    \caption{Experiment GG. Weibull Fit}
    \label{fig:w3}
\end{figure}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=4in]{img/kinect.png}
    \caption{EvoDraw Instalation on Alife XV Cancun Mexico.}
    \label{fig:kinect}
\end{figure}

>>>>

% IEAs
Interactive evolutionary computation (IEC) systems are, in general, evolutionary methods
whose fitness evaluations are performed by humans through an interactive 
system \cite{eiben2015interactive}.
They are usually applied in problems where the fitness function is not known or simply
does not exist, and the result of optimization should fit a certain human need or desire such as an aesthetic ideal.  
That is why their use cases includes the evolution of objects with subjective characteristics
such as visual appeal or attractiveness \cite{biomorphs} as well as others where human behavior is 
considered, for instance the optimization of teamwork \cite{kosorukoff2002evolutionary}
or creativity \cite{yu2011cooks}. In the cases when 
human interaction is responsible of other 
aspects of the evolutionary process, some authors classify these IEC methods 
as human-based evolutionary computation \cite{kosorukoff2001human} 
or as human-based computation \cite{quinn2011human}.

% Human Based Computation
IEC systems are an interesting venue of research, since they have demonstrated 
their ability for effectively 
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992,evoeco},
as well as other types of artifacts in many other domains \cite{ie1}. 
% Problems
However, the necessary intervention of humans brings certain challenges 
to designers of IEC methods; namely, human evaluations are scarce, slow and expensive, there is
human fatigue caused by the interaction \cite{ie1}, and also boredom arises
when users evaluate a large number of phenotypes, 
many of which are not interesting or are very similar to each other.
% C-IEAs
Moreover, the performance of these systems effectively depends on the number of users
they are able to include; to reach more users,
IEC systems are some times developed as web applications depending on web visitors to help
with the search, using both anonymous and registered users. Some systems 
employ a collaborative technique, where several users participate in 
the evaluation, this method is called Collaborative-IEC (C-IEC)
\cite{picbreeder,seyama2016development,wagy2014collective}.
% Volunteers 
Including an IEC in a volunteer system can lower the requirements for
participants in the experiment thus increasing the {\em performance} of the whole system. But using a volunteer based 
system raises other issues \cite{sarmenta2001volunteer,web:BOINC}, such as the 
volunteer\'s lack of accountability, and the need to build trust between participants and project
owners. Other issues for project owners are also the difficulty of predicting 
the amount of time and resources a volunteer is willing to spend on the system, 
and how they decide if they participate or not \cite{JJ:2016}.

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=6in]{img/framework.eps}
    \caption{IEC Human-centered framework.}
    \label{fig:hc_framework}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Experiment G. Weibull Fit}
    \label{fig:w2}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Experiment GG. Weibull Fit}
    \label{fig:w3}
\end{figure}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.3in]{img/kinect.png}
    \caption{EvoDraw Instalation on Alife XV Cancun Mexico.}
    \label{fig:kinect}
\end{figure}
